Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-10-13 algo-best-alt.tex
petite revision section label th.

\noindent
We show now the existence of a path $\pi$ of Lemma~\ref{lem:algo-completeness}, 
by simultaneous induction on $n_{q, q'}$ and $n_{q, p, q'}$.

The base case, $n = 0$ corresponds to $t = \varepsilon$. 
In this case, by~\eqref{eq:SWVPA-weight}, $b_\top(q, p, q') = \zero$,
$b_\bot(q, q) = \one$ and $b_\bot(q, q') = \zero$ if $q \neq q'$.

>>>>

\noindent
We show now the existence of a path $\pi$ as expected, %in Lemma~\ref{lem:algo-complete}, 
by simultaneous induction on $n_{q, q'}$ and $n_{q, p, q'}$.

\noindent
The base case, $n = 0$ corresponds to $t = \varepsilon$. 
In this case, by~\eqref{eq:SWVPA-weight}, $b_\top(q, p, q') = \zero$,
$b_\bot(q, q) = \one$ and $b_\bot(q, q') = \zero$ if $q \neq q'$.
